Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
More citations

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case in
\cref{section:definitions}). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem
\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

>>>>

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. This is used in many areas, including bioinformatics \citep{Bonnici:2013},
computer vision \citep{cviu11,pr15}, malware detection \citep{DBLP:conf/dimva/BruschiMM06},
compilers \citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
\citep{Conte:2004}.  The problem comes in two forms: in the non-induced variant, edges must be
mapped to edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges
may only be mapped to non-edges.

When a pattern cannot be found, we may wish to be given a result which maps as many vertices of the
pattern into the target as possible. In the induced case, this is known as the maximum common
induced subgraph problem (we discuss the non-induced case in \cref{section:definitions}). However,
although recent subgraph isomorphism algorithms are comfortable working with graphs with thousands
of vertices, the state of the art for the maximum common subgraph problem
\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.
